My title

### 2024-11-04 paper/paper.qmd
updated paper and references

library(tidyverse)
library(caret)
library(glmnet)
library(nnet)
library(lubridate)
library(pROC)
library(stringr)
```

@@

The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored. The distributions of the variables is as follows:

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

```{r}

@@

```{r}

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}

>>>>

library(tidyverse)
library(caret)
library(glmnet)
library(nnet)
library(lubridate)
library(pROC)
library(stringr)
library(gt)
```

@@

The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored. The poll end dates were included to capture the temporal changes in candidates' support rate. Transparency score was selected as an identification of the polls' trustworthiness, which must be controlled for in the analysis. Other variables representing the poll quality in the raw dataset, such as the poll score and the FiveThirtyEight rating, were excluded from the models for two reasons. First, the documentation by FiveThirtyEight suggests that the numeric rating, poll score, and transparency score are highly related [@5382]. Second, the data cleaning process filtered data points with high FiveThirtyEight ratings and poll scores. The distributions of selected variables are as follows:

@@

The goal of our modelling strategy is twofold. Firstly, we seek to predict the winning candidate on election day by calculating the expected win rate of Vice President Kamala Harris and Former President Donald Trump in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, and Nevada [@nyt2024polls]. Secondly, we hope to predict the candidate who has the popular vote on election day, controlling for the potential bias of national polls by accounting for the difference between polled popular vote and the actual popular vote on election day for the 2020 cycle.

To achieve the first goal, the polls dataset was divided by individual states, and only data points from the seven swing states were selected, forming seven smaller datasets. Then, for each state, the harris_win variable was constructed by comparing the support rate of the candidates in each poll. The variable was set to 1 if the support rate of Harris is greater than or equal to Trump's support rate and 0 when Trump's support rate is greater. A logistic model was constructed for each state, using harris_win as the outcome and previously stated predictors as inputs. [EXPLAIN THE PROBABILITY STEP HERE]

For the popular vote, we utilized the data from 2020 to calculate each pollster's bias by identifying the average difference between the popular vote on election day and their polled national support rates of Trump and President Joe Biden. Next, we adjusted the polled national support rates of pollsters in the 2024 cycle by the calculated gap in 2020. By making this adjustment, we are assuming that the pollsters systematically bias 2024 candidates equally compared to 2020 candidates. We acknowledge that the assumption is most likely false. Ideally, incorporating poll data from earlier election cycles may produce a more accurate indicator of how pollsters systematically bias candidates from the two dominant political parties. However, comprehensive poll data before 2020 is unavailable. Since popular vote is unrelated to the winner of the election, we are using this analysis as an exploration of methods that incorporate historical data without emphasizing predictiveness. Using both adjusted and unadjusted national support levels, multiple linear regressions were created with support levels as the outcome and stated predictors as inputs to predict candidates' support rate over time. Adjusted and unadjusted logistic regressions were made using harris_win as the outcome and the same predictors to predict the candidate with the popular vote on election day. The attempt to control for historical bias was not applied to the swing states due to a lack of data.

@@

### Logistic models
Define $y_i$ as the binary outcome variable indicating whether Harris wins (1) or not (0) for the $i^{th}$ observation. $x_{1i}$ is the end_date for the $i^{th}$ observation. $x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation. $x_{3i}$ is the transparency_score for the $i^{th}$ observation. $x_{4i}$ is the sample_size for the $i^{th}$ observation.

The logistic regression model can be expressed as follows:

\begin{align} y_i &\sim \text{Bernoulli}(p_i) 
\\ \text{logit}(p_i) &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}

Line (1) specifies that the outcome variable $y_i$ follows a Bernoulli distribution with probability $p_i$ of success (i.e., Harris winning). Line (2) links the linear combination of predictors to the probability $p_i$, where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable above.

This logistic regression model was applied independently to the data on each swing state and the adjusted and unadjusted popular vote polls.

### Multiple linear regression models
Define $y_i$ as the percentage national support for Harris or Trump for the $i^{th}$ observation. $x_{1i}$ is the end_date for the $i^{th}$ observation. $x_{2i}$ is the binary value of has_sponsor for the $i^{th}$ observation. $x_{3i}$ is the transparency_score for the $i^{th}$ observation. $x_{4i}$ is the sample_size for the $i^{th}$ observation.

The multiple linear regression model can be expressed as follows:

\begin{align} y_i &= \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \beta_3 x_{3i} + \beta_4 x_{4i} \end{align}

Where $\beta_0$ is the intercept term, and $\beta_1, \beta_2, \beta_3, \beta_4$ are coefficients corresponding to each predictor variable.

Separate multiple linear regression models were applied to the polled national support rate of Harris and Trump, with and without adjustments from historical data.

@@

We decided to use a logistic model to predict the winner on election day because it directly outputs candidates' chance of winning each swing state, enabling us to use a probabilistic function to identify their overall chance of winning. Comparatively, a linear regression model merely predicts the level of support for candidates, which fails to identify a winner.

# Regional polls analysis
trump_2024_regional <- trump_2024_lower %>% filter(state != "National")
harris_2024_regional <- harris_2024_lower %>% filter(state != "National")

trump_Pennsylvania <- trump_2024_regional %>% filter(state == "Pennsylvania")
trump_Georgia <- trump_2024_regional %>% filter(state == "Georgia")
trump_North_Carolina <- trump_2024_regional %>% filter(state == "North Carolina")
trump_Michigan <- trump_2024_regional %>% filter(state == "Michigan")
trump_Arizona <- trump_2024_regional %>% filter(state == "Arizona")
trump_Wisconsin <- trump_2024_regional %>% filter(state == "Wisconsin")
trump_Nevada <- trump_2024_regional %>% filter(state == "Nevada")

harris_Pennsylvania <- harris_2024_regional %>% filter(state == "Pennsylvania")
harris_Georgia <- harris_2024_regional %>% filter(state == "Georgia")
harris_North_Carolina <- harris_2024_regional %>% filter(state == "North Carolina")
harris_Michigan <- harris_2024_regional %>% filter(state == "Michigan")
harris_Arizona <- harris_2024_regional %>% filter(state == "Arizona")
harris_Wisconsin <- harris_2024_regional %>% filter(state == "Wisconsin")
harris_Nevada <- harris_2024_regional %>% filter(state == "Nevada")

combined_Pennsylvania <- full_join(
  trump_Pennsylvania,
  harris_Pennsylvania,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Georgia <- full_join(
  trump_Georgia,
  harris_Georgia,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_North_Carolina <- full_join(
  trump_North_Carolina,
  harris_North_Carolina,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Michigan <- full_join(
  trump_Michigan,
  harris_Michigan,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Arizona <- full_join(
  trump_Arizona,
  harris_Arizona,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Wisconsin <- full_join(
  trump_Wisconsin,
  harris_Wisconsin,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_Nevada <- full_join(
  trump_Nevada,
  harris_Nevada,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

# mutate harris_win variable by comparing polled support rates
# preparing data for logistic regression
combined_Pennsylvania <- combined_Pennsylvania %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_Georgia <- combined_Georgia %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_North_Carolina <- combined_North_Carolina %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_Michigan <- combined_Michigan %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_Arizona <- combined_Arizona %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_Wisconsin <- combined_Wisconsin %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

combined_Nevada <- combined_Nevada %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

# Create 7 different logistic regressions to predict Harris's win rate
# in each state
logistic_Pennsylvania <- readRDS(here::here("models/Logistic_model_Pennsylvania.rds"))

logistic_Georgia <- readRDS(here::here("models/Logistic_model_Georgia.rds"))

logistic_North_Carolina <- readRDS(here::here("models/Logistic_model_North_Carolina.rds"))

logistic_Michigan <- readRDS(here::here("models/Logistic_model_Michigan.rds"))

logistic_Arizona <- readRDS(here::here("models/Logistic_model_Arizona.rds"))

logistic_Wisconsin <- readRDS(here::here("models/Logistic_model_Wisconsin.rds"))

logistic_Nevada <- readRDS(here::here("models/Logistic_model_Nevada.rds"))

# test logistic models for state specific analysis
# mutate fitted values

combined_Pennsylvania <- combined_Pennsylvania %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Pennsylvania, type = "response"), 2)
  )

roc_obj_Pennsylvania <- roc(combined_Pennsylvania$harris_win,
                  combined_Pennsylvania$harris_win_prob)

auc_value_Pennsylvania <- auc(roc_obj_Pennsylvania)

combined_Georgia <- combined_Georgia %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Georgia, type = "response"), 2)
  )

roc_obj_Georgia <- roc(combined_Georgia$harris_win,
                            combined_Georgia$harris_win_prob)

auc_value_Georgia <- auc(roc_obj_Georgia)

combined_North_Carolina <- combined_North_Carolina %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_North_Carolina, type = "response"), 2)
  )

roc_obj_North_Carolina <- roc(combined_North_Carolina$harris_win,
                            combined_North_Carolina$harris_win_prob)

auc_value_North_Carolina <- auc(roc_obj_North_Carolina)

combined_Michigan <- combined_Michigan %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Michigan, type = "response"), 2)
  )

roc_obj_Michigan <- roc(combined_Michigan$harris_win,
                            combined_Michigan$harris_win_prob)

auc_value_Michigan <- auc(roc_obj_Michigan)

combined_Arizona <- combined_Arizona %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Arizona, type = "response"), 2)
  )

roc_obj_Arizona <- roc(combined_Arizona$harris_win,
                            combined_Arizona$harris_win_prob)

auc_value_Arizona <- auc(roc_obj_Arizona)

combined_Wisconsin <- combined_Wisconsin %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Wisconsin, type = "response"), 2)
  )

roc_obj_Wisconsin <- roc(combined_Wisconsin$harris_win,
                            combined_Wisconsin$harris_win_prob)

auc_value_Wisconsin <- auc(roc_obj_Wisconsin)

combined_Nevada <- combined_Nevada %>%
  mutate(
    harris_win_prob = round(100*predict(logistic_Nevada, type = "response"), 2)
  )

roc_obj_Nevada <- roc(combined_Nevada$harris_win,
                            combined_Nevada$harris_win_prob)

auc_value_Nevada <- auc(roc_obj_Nevada)

We identified the AUC values and ROC plots for each of the seven swing-state logistic regressions. The ROC plots are presented in the Appendix, from @fig-pen to @fig-nev. The AUC values are: 0.90 for Pennsylvania, 0.88 for Georgia, 0.74 for North Carolina, 0.93 for Michigan, 1.00 for Arizona, 0.86 for Wisconsin, and 0.65 for Nevada. All states other than Nevada have acceptable or excellent AUC values, indicating that the respective logistic models are reliable when distinguishing cases where Harris wins. The low AUC value for Nevada is potentially caused by the limited sample size; there are only 9 polls conducted in Nevada.

Moreover, the sample size restrictions were the reason why we did not use training and testing data to validate our logistic models. The state with the greatest number of polls, Pennsylvania, only records 26 polls. Utilizing training and testing datasets implies that the datasets may include only a couple of data points in some states, which is insufficient to construct or test the model. On top of that, according to [@trainingerror], achieving low training error is sufficient to ensure the predictability of a model to some extent. [ADD MORE IF NECESSARY]

# find biases of pollsters from 2020 national polls data
# filter out national polls from the datasets
trump_2024_national <- trump_2024 %>% filter(state == "National")
harris_2024_national <- harris_2024 %>% filter(state == "National")
trump_2020_national <- trump_2020 %>% filter(state == "National")
biden_2020_national <- biden_2020 %>% filter(state == "National")

# Define actual results
actual_results_2020 <- list(Trump_pct = 47, Biden_pct = 51)

# Calculate bias per pollster
rep_pollster_bias <- trump_2020_national %>%
  group_by(pollster) %>%
  summarize(
    Trump_bias = mean(pct - actual_results_2020$Trump_pct, na.rm = TRUE)
  )

dem_pollster_bias <- biden_2020_national %>%
  group_by(pollster) %>%
  summarize(
    Biden_bias = mean(pct - actual_results_2020$Biden_pct, na.rm = TRUE)
  )

# adjust 2024 national polls percentages by the average pollster biases
# also mutate has_sponsor variable into dummy variable and remove NA's
trump_2024_national_adj <- trump_2024_national %>%
  left_join(rep_pollster_bias, by = "pollster") %>%
  mutate(
    pct_adj = pct - ifelse(!is.na(Trump_bias), Trump_bias, 0)
  ) %>%
  select(-Trump_bias)

# Adjust Harris 2024 National Polls
harris_2024_national_adj <- harris_2024_national %>%
  left_join(dem_pollster_bias, by = "pollster") %>%
  mutate(
    pct_adj = pct - ifelse(!is.na(Biden_bias), Biden_bias, 0)
  ) %>%
  select(-Biden_bias)

# model adjusted support percentage by time and control variables
# first split training and testing dataset using an 80/20 split
set.seed(11451)
trainIndex_trump_adj <- createDataPartition(trump_2024_national_adj$pct_adj, 
                                        p = 0.8, list = FALSE)
data_train_trump_adj <- trump_2024_national_adj[trainIndex_trump_adj, ]
data_test_trump_adj  <- trump_2024_national_adj[-trainIndex_trump_adj, ]

trainIndex_harris_adj <- createDataPartition(harris_2024_national_adj$pct_adj, 
                                         p = 0.8, list = FALSE)
data_train_harris_adj <- harris_2024_national_adj[trainIndex_harris_adj, ]
data_test_harris_adj  <- harris_2024_national_adj[-trainIndex_harris_adj, ]

model_date_harris_adj <- lm(pct_adj ~ end_date + has_sponsor +
                          transparency_score + sample_size, data = data_train_harris_adj)
model_date_trump_adj <- lm(pct_adj ~ end_date + has_sponsor +
                         transparency_score + sample_size, data = data_train_trump_adj)

# repeat for unadjusted support levels
trainIndex_trump <- createDataPartition(trump_2024_national$pct, 
                                        p = 0.8, list = FALSE)
data_train_trump <- trump_2024_national[trainIndex_trump, ]
data_test_trump  <- trump_2024_national[-trainIndex_trump, ]

trainIndex_harris <- createDataPartition(harris_2024_national$pct, 
                                         p = 0.8, list = FALSE)
data_train_harris <- harris_2024_national[trainIndex_harris, ]
data_test_harris  <- harris_2024_national[-trainIndex_harris, ]

model_date_harris <- lm(pct ~ end_date + has_sponsor +
                          transparency_score + sample_size, data = data_train_harris)
model_date_trump <- lm(pct ~ end_date + has_sponsor +
                         transparency_score + sample_size, data = data_train_trump)

# Functions to evaluate model using testing dataset
evaluate_model_adj <- function(model, test_data) {
  predictions <- predict(model, newdata = test_data)
  actuals <- test_data$pct_adj
  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
  r_squared <- summary(model)$r.squared
  return(list(RMSE = rmse, R_squared = r_squared))
}

evaluate_model <- function(model, test_data) {
  predictions <- predict(model, newdata = test_data)
  actuals <- test_data$pct
  rmse <- sqrt(mean((predictions - actuals)^2, na.rm = TRUE))
  r_squared <- summary(model)$r.squared
  return(list(RMSE = rmse, R_squared = r_squared))
}

# Evaluate Harris model with adjusted support percentages
harris_evaluation_adj <- evaluate_model_adj(model_date_harris_adj, data_test_harris_adj)

# Evaluate Trump model with adjusted support percentages
trump_evaluation_adj <- evaluate_model_adj(model_date_trump_adj, data_test_trump_adj)

# Evaluate Harris model with unadjusted support percentages
harris_evaluation <- evaluate_model(model_date_harris, data_test_harris)

# Evaluate Trump model with unadjusted support percentages
trump_evaluation <- evaluate_model(model_date_trump, data_test_trump)

# Augment data with model predictions
model_harris_adj <- readRDS(here::here("models/MLR_adjusted_harris.rds"))
model_trump_adj <- readRDS(here::here("models/MLR_adjusted_trump.rds"))

harris_2024_national_adj <- harris_2024_national_adj %>% mutate(
  fitted_date = predict(model_harris_adj)
)

trump_2024_national_adj <- trump_2024_national_adj %>% mutate(
  fitted_date = predict(model_trump_adj)
)

# Unadjusted datasets
model_harris <- readRDS(here::here("models/MLR_harris.rds"))
model_trump <- readRDS(here::here("models/MLR_trump.rds"))

harris_2024_national <- harris_2024_national %>% mutate(
  fitted_date = predict(model_harris)
)

trump_2024_national <- trump_2024_national %>% mutate(
  fitted_date = predict(model_trump)
)

# evaluate models without using training and testing data
harris_eval_adj <- evaluate_model_adj(model_harris_adj, harris_2024_national_adj)

harris_eval <- evaluate_model(model_harris, harris_2024_national)

trump_eval_adj <- evaluate_model_adj(model_trump_adj, trump_2024_national_adj)

trump_eval <- evaluate_model(model_trump, trump_2024_national)

#### Logistic regression for national support ####

combined_national <- full_join(
  trump_2024_national,
  harris_2024_national,
  by = c("pollster", "has_sponsor", "pollscore", 
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_national <- combined_national %>% mutate(
  harris_win = case_when(
    pct.y >= pct.x ~ 1,
    pct.y < pct.x ~ 0
  )
)

# repeat for adjusted support levels
combined_national_adj <- full_join(
  trump_2024_national_adj,
  harris_2024_national_adj,
  by = c("pollster", "has_sponsor", "pollscore",
         "transparency_score", "sample_size", "end_date", "state", "cycle")
)

combined_national_adj <- combined_national_adj %>% mutate(
  harris_win = case_when(
    pct_adj.y >= pct_adj.x ~ 1,
    pct_adj.y < pct_adj.x ~ 0
  )
)

# logistic model to predict the popular vote
model_logistic <- readRDS(here::here("models/Logistic_model.rds"))

model_logistic_adj <- readRDS(here::here("models/Logistic_model_adjusted.rds"))

# include predicted outcomes to the dataframes
combined_national <- combined_national %>%
  mutate(
    harris_win_prob = round(100*predict(model_logistic, type = "response"), 2)
  )

combined_national_adj <- combined_national_adj %>%
  mutate(
    harris_win_prob = round(100*predict(model_logistic_adj, 
                                        type = "response"), 2)
  )

#### Evaluate the Model ####

# ROC Curve and AUC
roc_obj <- roc(combined_national$harris_win,
               combined_national$harris_win_prob)
auc_value <- auc(roc_obj)

roc_obj_adj <- roc(combined_national_adj$harris_win,
               combined_national_adj$harris_win_prob)
auc_value_adj <- auc(roc_obj_adj)
```
For the analysis of the national popular vote, the logistic model of adjusted polls possess an AUC value of 0.98, and the logistic model of unadjusted polls have an AUC of 0.94, indicating high reliability of categorization. Their respective ROC plots are presented as @fig-log and @fig-logadj.

RMSE values and R squared values were calculated for the multiple linear regression models predicting popular vote. The RMSE values for all four models, adjusted and unadjusted support levels of the two candidates, are greater than 1, indicating that the fitted values and the support levels of actual polls are more than 1 percent apart on average, which is significant when analyzing popular vote. Moreover, all R squared values other than the model for the adjusted support rate of Trump, are smaller than 0.3, indicating the inability of the models to account for the variance of national support rates in the data. The model for the adjusted support rate of Trump has a R squared value of 0.69, indicating a relatively high proportion of variance in polled support rates being explained by the multiple linear regression model. This was expected, as the predictors such as a poll's end date and transparency does not necessarily correlate with the outcome of the polls. More predictive variables used by FiveThirtyEight [@5383] for their predictions are unavailable in the raw dataset, which is a key limitation of the data.

@@

```{r}
# plot model predictions
# combine the datasets to create a single visual
combined_data_adj <- bind_rows(harris_2024_national_adj, trump_2024_national_adj)
combined_data <- bind_rows(harris_2024_national, trump_2024_national)

# create the plot that contains scattered points of adjusted percentages
# and lines for fitted values
ggplot(combined_data_adj, aes(x = end_date, y = pct_adj, color = candidate_name)) +
  # Scatter points for actual adjusted percentages
  geom_point(alpha = 0.6) +
  # Regression lines
  geom_line(aes(y = fitted_date), size = 0.5) +
  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
  # Assign specific colors
  scale_color_manual(values = 
                       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  # Customize the plot appearance
  theme_classic() +
  labs(
    y = "Adjusted Percent Support",
    x = "End Date",
    title = "Multiple Linear Models for Harris and Trump (2024)",
    color = "Candidate"
  ) +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

# Unadjusted support percentages
ggplot(combined_data, aes(x = end_date, y = pct, color = candidate_name)) +
  # Scatter points for actual adjusted percentages
  geom_point(alpha = 0.6) +
  # Regression lines
  geom_line(aes(y = fitted_date), size = 0.5) +
  xlim(as.Date("2024-07-19"), as.Date("2024-10-25")) +
  # Assign specific colors
  scale_color_manual(values = 
                       c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  # Customize the plot appearance
  theme_classic() +
  labs(
    y = "Adjusted Percent Support",
    x = "End Date",
    title = "Multiple Linear Models for Harris and Trump (2024)",
    color = "Candidate"
  ) +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

@@

```{r}
summary(model_logistic)
summary(model_logistic_adj)
```

@@

```{r}
#| label: fig-pen
#| fig-cap: ROC Curve for Harris Win Prediction, Pennsylvania
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Pennsylvania)

@@

```{r}
#| label: fig-geo
#| fig-cap: ROC Curve for Harris Win Prediction, Georgia
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Georgia)

```{r}
#| label: fig-nor
#| fig-cap: ROC Curve for Harris Win Prediction, North Carolina
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_North_Carolina)

```{r}
#| label: fig-mic
#| fig-cap: ROC Curve for Harris Win Prediction, Michigan
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Michigan)

```{r}
#| label: fig-ari
#| fig-cap: ROC Curve for Harris Win Prediction, Arizona
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Arizona)

```{r}
#| label: fig-wis
#| fig-cap: ROC Curve for Harris Win Prediction, Wisconsin
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Wisconsin)

```{r}
#| label: fig-nev
#| fig-cap: ROC Curve for Harris Win Prediction, Nevada
#| echo: false
#| message: false
#| warning: false

plot(roc_obj_Nevada)

```{r}
#| label: fig-log
#| fig-cap: ROC Curve for Popular Vote Prediction
#| echo: false
#| message: false
#| warning: false

plot(roc_obj)

```{r}
#| label: fig-logadj
#| fig-cap: ROC Curve for Popular Vote Prediction, Adjusted
#| echo: false
#| message: false
#| warning: false

plot(roc_obj)
